\textit{MSF: Modulated Sub-graph Finder}

### 2018-03-19 MSF_Paper.tex
create make file; implement F1000 style; fix reference; write abstract; externalize reference

	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Documents/PhDThesis/MSFPaper/Tgfb1}
		\caption{Input}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Documents/PhDThesis/MSFPaper/TGFBstep1}
		\caption{Step 1}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Documents/PhDThesis/MSFPaper/TGFBstep2}
		\caption{Step 2}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Documents/PhDThesis/MSFPaper/TGFBstep3}
		\caption{Step 3}
	\end{subfigure}
	\caption{Overview of \texttt{MSF} process showing 3 step toy example to identify the modulated sub-graphs. (a) Input: showing a network of genes with green nodes as genes with \textit{p}-values $< $ 0.05, and blue nodes are genes with \textit{p}-values $>$ 0.05, (b) Step 1: genes circled red show the two initial modulated sub-graphs identified, sub-graph 1 with genes M,K,C and sub-graph 2 with genes S,V,T, (c) Step 2: shows the modulated sub-graph 1 being extended to M,K,C,A,D while no extension in sub-graph 2 (d) Step 3: shows both the modulated sub-graphs merging together with the addition of 3 genes Z,W,P.}
			\end{minipage}
}
\end{figure*}

\begin{figure*}[p]
	\centering
	\fbox{
		\begin{minipage}{17 cm}
			\includegraphics[width=16cm]{Documents/PhDThesis/MSFPaper/DEGvsMSF2}
			\caption{Graph shows the percentage of DEG analysis genes and MSF identified sub-graph genes recall rates 100 times for the three different time points after the addition of Poisson distributed noise.}
			\label{label}
		\end{minipage}
	}
\end{figure*}

\begin{figure*}
	\centering
	\fbox{
		\begin{minipage}{17 cm}
	\includegraphics[width=1.05\linewidth]{ModulatesSubPaths/MSFData/Ebola6H/SeperatedMergedNetwork}
	\caption{Shows the three modulated sub-graphs identified by MSF at 6hpi, where nodes are genes and edges are the interactions. The node coloring is associated to KEGG pathways referring to the colors in the legend. The graph edges are from Reactome. Important genes to EBOV infection as from literature are enlarged in the graph. The signal flow corresponding to each sub-graph is depicted as simple flow chart against each sub-graph.}
		\end{minipage}
}
\end{figure*}

>>>>

	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Tgfb1.png}
		\caption{Input}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{TGFBstep1.png}
		\caption{Step 1}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{TGFBstep2.png}
		\caption{Step 2}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{TGFBstep3.png}
		\caption{Step 3}
	\end{subfigure}
	\caption{Overview of \texttt{MSF} process showing 3 step toy example to identify the modulated sub-graphs. (a) Input: showing a network of genes with green nodes as genes with \textit{p}-values $< $ 0.05, and blue nodes are genes with \textit{p}-values $>$ 0.05, (b) Step 1: genes circled red show the two initial modulated sub-graphs identified, sub-graph 1 with genes M,K,C and sub-graph 2 with genes S,V,T, (c) Step 2: shows the modulated sub-graph 1 being extended to M,K,C,A,D while no extension in sub-graph 2 (d) Step 3: shows both the modulated sub-graphs merging together with the addition of 3 genes Z,W,P.}
			\end{minipage}
}
\end{figure*}

\begin{figure*}[p]
	\centering
	\fbox{
		\begin{minipage}{17 cm}
			\includegraphics[width=16cm]{DEGvsMSF2.png}
			\caption{Graph shows the percentage of DEG analysis genes and MSF identified sub-graph genes recall rates 100 times for the three different time points after the addition of Poisson distributed noise.}
			\label{label}
		\end{minipage}
	}
\end{figure*}

\begin{figure*}
	\centering
	\fbox{
		\begin{minipage}{17 cm}
	\includegraphics[width=1.05\linewidth]{SeperatedMergedNetwork.png}
	\caption{Shows the three modulated sub-graphs identified by MSF at 6hpi, where nodes are genes and edges are the interactions. The node coloring is associated to KEGG pathways referring to the colors in the legend. The graph edges are from Reactome. Important genes to EBOV infection as from literature are enlarged in the graph. The signal flow corresponding to each sub-graph is depicted as simple flow chart against each sub-graph.}
		\end{minipage}
}
\end{figure*}
